The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
69 vir

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots of this form, though for $\rho$~Leonis all variability is consistent with red noise \citep{Aerts2018,bowman19}.}
\label{fig:rholeo}
\end{figure*}

@@

The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}. Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 5 onwards. Target selection was performed by cross-matching Hipparcos \citep{leeuwen07} with the K2 Ecliptic Plane Input Catalog \citep[EPIC,][]{huber16} and selecting all targets on silicon brighter than $Kp < 6$ on silicon. M~giants which pulsate with periods that are long compared to a K2 campaign were removed. We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of solar-like oscillations cannot be sufficiently sampled with long-cadence data.

 Some very bright stars were observed with conventional apertures as part of these programs, but we exclude them from the present discussion and data release, which is oriented towards targets only observable with halo photometry. 
% normal apertures in 6
We include $\alpha$\,Vir (Spica), which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture. In Campaign~6 it was assigned a normal aperture due an erroneous estimate of its \kepler magnitude and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline. The stars in Campaign~18 in our sample were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5. A possible further extension of the present work would be to recover C5 light curves for these objects using smear and/or modified halo photometry.

>>>>

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: Lomb-Scargle power spectra in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots of this form; in $\rho$~Leo, variability is attributed to red noise and a 26.8~d rotation period \citep{Aerts2018,bowman19}.}
\label{fig:rholeo}
\end{figure*}

@@

The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}. Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 6 onwards. Target selection was performed by cross-matching Hipparcos \citep{leeuwen07} with the K2 Ecliptic Plane Input Catalog \citep[EPIC,][]{huber16} and selecting all targets on silicon brighter than $Kp < 6$ on silicon. M~giants which pulsate with periods that are long compared to a K2 campaign were removed. We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of oscillations cannot be sufficiently sampled with long-cadence data, such as for $\delta$~Sct stars whose maximum frequencies can exceed the long-cadence Nyquist limit.

 Some very bright stars were observed with conventional apertures as part of these programs, but we exclude them from the present discussion and data release, which is oriented towards targets only observable with halo photometry. 
% normal apertures in 6
We include $\alpha$\,Vir (Spica) and 69~Vir, which were observed in Campaign~6 without a halo aperture (in Campaign~17 Spica was re-observed, with a halo aperture). In Campaign~6 they were assigned normal apertures due an erroneous estimate of their \kepler magnitudes and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline. The stars in Campaign~18 in our sample were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5. A possible further extension of the present work would be to recover C5 light curves for these objects using smear and/or modified halo photometry.
